---
title: "Toy_Store_E -- Data Analysis"
author: "Colten Wright"
format: 
  revealjs:
    embed-resources: true
    slide-number: true
    smaller: true
    footer: Toy_store_E Analysis
---

```{r}
library(tidyverse)
library(dplyr)
library(DBI)
library(RPostgres)
library(lubridate)
library(viridis)
library(RColorBrewer)
```

```{r}
connection <- dbConnect(
  RPostgres::Postgres(),
  dbname = "toy_stor_e",
  host = "localhost",
  port = 5432,
  user = "**",
  password = "***")
```

```{r}
orders <- dbReadTable(connection, 'orders')
order_items <- dbReadTable(connection, 'order_items')
products <- dbReadTable(connection, 'products')
order_item_refunds <- dbReadTable(connection, 'order_item_refunds')
website_sessions <- dbReadTable(connection, 'website_sessions')
```



## Overview
- Slides 3-5: Website Analysis
- Slides 6-9: Advertisement/Campaign Analysis
- Slides 10-13: Refund Analysis

## What is the general trend of orders?
```{r}
## Line plot of number of orders over time


# Query created in SQL 
website_usage_and_orders <- dbGetQuery(connection, "
SELECT
EXTRACT(YEAR from created_at) AS year,
EXTRACT(MONTH from created_at) AS month,
COUNT(order_id) AS number_of_orders
FROM orders
GROUP BY EXTRACT(YEAR from created_at), Extract(MONTH from created_at)
ORDER BY EXTRACT(YEAR from created_at), Extract(MONTH from created_at);
")

website_usage_and_orders %>%
  mutate(date = make_date(year, month, 1)) %>%
  ggplot(aes(x = date, y= number_of_orders))+
  geom_line(color = 'darkblue')+
  xlab('Date')+
  ylab('Number of Orders')
  
```





```{r,include=FALSE}
## Regression of device type and whether there was an order or not
joined_tables <- website_sessions %>%
  left_join(orders, by = join_by(website_session_id)) %>%
  mutate(completed_order = if_else(is.na(order_id), 0, 1))
model <- glm(completed_order ~ device_type, data = joined_tables, family = binomial)

summary(model)
exp(coef(model))
exp(confint(model))
levels(as.factor(joined_tables$device_type))

```

## Does the Device Used Affect Order Rate?


After Running a logistic regression model, it was found that:
  
::: {.incremental}

  - P Value:  < .0001
  - This means that the percentage of website usages that result in an order are significantly different between mobile users and computer users.
  - It turns out that computer users have roughly  65.7% higher odds of completing an order than mobile users do!
  
:::


## A Deeper Dive
```{r}
## Bar chart of device type and rate at which orders are made
joined_tables %>%
group_by(device_type) %>%
  summarise(sessions = n(),
            orders = sum(completed_order),
            order_rate = mean(completed_order),
            .groups = "drop") %>%
  ggplot(aes(x = device_type, y= order_rate, fill = device_type))+
  geom_col()+
  scale_fill_brewer(palette = 'Dark2')+
  scale_x_discrete(labels = c('Computer Orders', 'Mobile Orders'))+
  xlab('Device Type')+
  ylab('Rate of Orders')+
  theme(legend.position = 'none')
```


# Advertisement

## Which Campaign leads to the most Orders?
```{r}
## utm campaign with number of orders


website_sessions %>%
  left_join(orders, by = join_by(website_session_id)) %>%
  group_by(month = floor_date(created_at.x, "month"), utm_campaign) %>%
  summarise(order_percentage = sum(!is.na(order_id)) / n()) %>%
  ungroup() %>%
  ggplot(aes(x = month, y = order_percentage, colour = utm_campaign))+
  geom_line()+
  xlab('Date')+
  ylab('Order Percentage')
  


```



```{r, include=FALSE}
## Regression of advertisement and whether there was an order or not
model1 <- glm(completed_order ~ utm_content, data = joined_tables, family = binomial)
summary(model1)
exp(coef(model1))
exp(confint(model1))
levels(as.factor(joined_tables$utm_content))


```
## Which Advertisements Led to More Orders?


After Running another logistic regression model, it was found that:


::: {.incremental}

  - P Value:  < .02 for all advertisements.
  
```{r, echo= TRUE}

exp(confint(model1))
```
  - These confidence intervals show that:
    - b_ad_2, g_ad_2, and No advertisement all have statistically significant evidence that they lead to more completed orders than the b_ad_1 does.
    - g_ad_1, and both social ads have statistically significant evidence that they lead to less completed orders than the b_ad_1.
  
:::



## Another Deeper Dive
```{r}
## Bar chart of advertisement and rate at which orders were made.

joined_tables %>%
  group_by(utm_content) %>%
  summarise(orders = sum(completed_order),
            order_rate = mean(completed_order),
            .groups = 'drop') %>%
  ggplot(aes(x = utm_content, y = order_rate, fill = utm_content))+
  geom_col()+
  scale_fill_brewer(palette = 'Set2')+
  scale_x_discrete(labels = c('b_ad_1', 'b_ad_2', 'g_ad_1', 'g_ad_2', 'No Ad', 'social_ad_1', 'social_ad_2'))+
  theme(legend.position = 'none')+
  xlab('Advertisement')+
  ylab('Order Rate')
```


# Refund Analysis

## A general idea of Refunds
```{r}
##Plot of Refunds over time
order_item_refunds %>%
  mutate(month = floor_date(created_at, "month")) %>%
  group_by(month) %>%
  summarise(refunds = n(), .groups = "drop") %>%
  ggplot(aes(x = month, y = refunds)) +
  geom_line(color= 'darkblue') +
  xlab("Date") +
  ylab("Number of Refunds")


```


## Do larger Orders Result in Larger Refunds?
```{r}
## Scatter plot of order value and refund amount
refund_by_order <- order_item_refunds %>%
  group_by(order_id) %>%
  summarise(
    total_refund = sum(refund_amount_usd),
    .groups = "drop")

order_value_refund <- orders %>%
  left_join(refund_by_order, by = "order_id") %>%
  mutate(total_refund = replace_na(total_refund, 0))

  ggplot(order_value_refund,
       aes(x = price_usd, y = total_refund)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  xlab("Order Value") +
  ylab("Total Refund Amount")
```


## What does a typical order look like?
```{r}
## Density plot of order value
orders %>%
  ggplot(aes(x = price_usd))+
  geom_density(linewidth = .75, color = 'darkblue')+
  geom_vline(xintercept = median(orders$price_usd, na.rm = TRUE), linetype = "dashed")+
  xlab('Price of Order')
```



# A Summary

## Key Ideas

::: {.incremental}

  - The number of orders generally increased over the study period, with notable seasonal spikes around     the holiday season.
  - Computer users had approximately 66% higher odds of completing an order than mobile users.
  - Advertisement performance varied across individual advertisement types, with several advertisements     showing statistically different odds of order completion compared with the reference advertisement,     b_ad_1.
  - b_ad_2 showed approximately 30% higher odds of order completion compared with b_ad_1.
  - The social advertisements showed substantially lower odds of order completion compared with b_ad_1.
  - The number of refunds generally increased over time, with a particularly large spike occurring in      September 2014








